Based on your instructions, I will create a LaTeX document that fills in the content for a Full Stack Developer role. Here is the completed code:

```tex
\documentclass[a4paper,12pt]{article}

\usepackage[left=0.65in,right=0.65in,top=0.7in,bottom=0.7in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{fontawesome5}
\usepackage{lmodern}
\usepackage{titlesec}
\usepackage{parskip}

% Colors
\definecolor{accent}{HTML}{1A73E8}

% Font
\renewcommand{\familydefault}{\sfdefault}

% Section Formatting
\titleformat{\section}{\large\bfseries\color{accent}}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{6pt}{4pt}

% Lists
\setlist[itemize]{leftmargin=*, itemsep=2pt, topsep=2pt}

\pagenumbering{gobble}

\begin{document}

%==========================
% HEADER
%==========================
\begin{center}
    {\Huge \textbf{\textcolor{accent}{mithrajith}}} \\[2pt]
    Samaya Puram, Trichy, Tamil Nadu, India \\[4pt]
    \faPhone\ 9566991632 \quad | \quad
    \href{https://www.linkedin.com/in/mithrajitks046}{\faLinkedin\ LinkedIn} \quad | \quad
    \href{https://github.com/mithrajith46}{\faGithub\ GitHub}
\end{center}

%==========================
% SUMMARY
%==========================
\section*{Summary}
Experienced Full Stack Developer with a strong background in building scalable web applications, machine learning models, and automation tools. Proficient in Python, JavaScript, backend logic, problem-solving, and delivering clean, maintainable solutions.

%==========================
% EDUCATION
%==========================
\section*{Education}
\textbf{B.Tech – Artificial Intelligence and Machine Learning} \\
Sri Shakthi Institute of Engineering and Technology, Coimbatore  
\hfill \textbf{2023–2027} \\
CGPA: 7.9

%==========================
% SKILLS
%==========================
\section*{Skills}
\textbf{Languages:} Python, JavaScript, HTML5, CSS3, Shell Scripting  
\textbf{Frameworks:} React.js, Flask, FastAPI  
\textbf{Databases:} MongoDB, PostgreSQL, MySQL  
\textbf{Machine Learning:} Scikit-learn, OpenCV, Pandas, NumPy  
\textbf{Tools:} Docker, Git/GitHub, VS Code, Linux  
\textbf{Other:} REST APIs, OOP, Data Structures, Generative AI, LLMs

%==========================
% PROJECTS
%==========================
\section*{Projects}

\textbf{AI Music Player}  
\textit{Machine Learning, Python}
\begin{itemize}
    \item Developed a music recommendation system that detects user mood and dynamically plays suitable songs.
    \item Integrated audio handling, playlist logic, and custom UI components for seamless interaction.
    \item Built using scikit-learn library for efficient model training.
\end{itemize}

\textbf{Project Hub}  
\textit{React.js, Node.js}
\begin{itemize}
    \item Designed a unified dashboard to organize academic and personal projects.
    \item Features include smart tagging, filtering, and version snapshots for tracking progress.
    \item Developed using React.js framework for efficient rendering.
\end{itemize}

\textbf{Campus Compass}  
\textit{Flask}
\begin{itemize}
    \item Created a college recommendation platform with custom scoring logic and input-based ranking.
    \item Added document upload support and auto-filtering to refine results.
    \item Built using Flask framework for rapid development.
\end{itemize}

\textbf{Student Leave Application Portal (SLAP)}  
\textit{Flask, MySQL}
\begin{itemize}
    \item Developed a complete leave management system with role-based access for students and faculty.
    \item Added approval workflows, notifications, and history logs for real-time tracking.
    \item Implemented using Flask framework for efficient routing.
\end{itemize}

\textbf{Web-App-Focuser}  
\textit{Shell, Batchfile}
\begin{itemize}
    \item Built a web application that helps users focus on their tasks by minimizing distractions.
    \item Implemented using Shell scripting and batch files for efficient automation.
    \item Developed custom UI components for seamless interaction.
\end{itemize}

\textbf{Tamil Brailli Frontend}  
\textit{JavaScript, Java, Shell}
\begin{itemize}
    \item Designed a frontend application that helps visually impaired users read Tamil texts.
    \item Implemented using JavaScript and Java technologies for efficient rendering.
    \item Built custom UI components for seamless interaction.
\end{itemize}

\textbf{Console Project}  
\textit{Python}
\begin{itemize}
    \item Developed a console-based application that helps users manage their daily tasks.
    \item Implemented using Python technology for rapid development.
    \item Built custom logic for efficient task management.
\end{itemize}

\end{document}
```

This document includes the required information and formatting. The projects section focuses on full-stack development with a mix of front-end and back-end technologies, along with machine learning and automation tools.