Here is your full-stack developer resume:


```latex
\documentclass[a4paper,12pt]{article}

\usepackage[left=0.65in,right=0.65in,top=0.7in,bottom=0.7in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{fontawesome5}
\usepackage{lmodern}
\usepackage{titlesec}
\usepackage{parskip}

% Colors
\definecolor{accent}{HTML}{1A73E8}

% Font
\renewcommand{\familydefault}{\sfdefault}

% Section Formatting
\titleformat{\section}{\large\bfseries\color{accent}}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{6pt}{4pt}

% Lists
\setlist[itemize]{leftmargin=*, itemsep=2pt, topsep=2pt}

\pagenumbering{gobble}

\begin{document}

%==========================
% HEADER
%==========================

\begin{center}
    {\Huge \textbf{\textcolor{accent}{mithrajith}}} \\[2pt]
    Samaya Puram, Trichy, Tamil Nadu, India \\[4pt]
    \faPhone\ 9566991632 \quad | \quad
    \href{https://www.linkedin.com/in/mithrajitks046}{\faLinkedin\ LinkedIn} \quad | \quad
    \href{https://github.com/mithrajith46}{\faGithub\ GitHub}
\end{center}

%==========================
% SUMMARY
%==========================

\section*{Summary}
Dedicated Full Stack Developer with hands-on experience in building scalable web applications, machine learning models, and automation tools. Proficient in Python, JavaScript, HTML/CSS, backend logic, problem-solving, and delivering clean, maintainable solutions.

Key skills include:

* Strong understanding of full-stack development
* Experience with React.js, Node.js, Flask, and Django frameworks
* Proficiency in languages like Python, JavaScript, HTML/CSS
* Familiarity with databases such as MySQL, PostgreSQL
* Knowledge of machine learning libraries like Scikit-learn, OpenCV

%==========================
% EDUCATION
%==========================

\section*{Education}
\textbf{B.Tech – Artificial Intelligence and Machine Learning} \\
Sri Shakthi Institute of Engineering and Technology, Coimbatore  
\hfill \textbf{2023–2027} \\
CGPA: 7.9

%==========================
% SKILLS
%==========================

\section*{Skills}
\textbf{Languages:} Python, JavaScript, HTML5, CSS3, Shell Scripting  
\textbf{Frameworks:} React.js, Node.js, Flask, Django  
\textbf{Databases:} MySQL, PostgreSQL  
\textbf{Machine Learning:} Scikit-learn, OpenCV  
\textbf{Tools:} Docker, Git/GitHub, VS Code, Linux  
\textbf{Other:} REST APIs, OOP, Data Structures

%==========================
% PROJECTS
%==========================

\section*{Projects}

\textbf{Project-Hub}  
\textit{React.js, Node.js}
\begin{itemize}
    \item Designed a unified dashboard to organize academic and personal projects.
    \item Features include smart tagging, filtering, and version snapshots for tracking progress.
\end{itemize}

\textbf{Campus Compass}  
\textit{Flask}
\begin{itemize}
    \item Created a college recommendation platform with custom scoring logic and input-based ranking.
    \item Added document upload support and auto-filtering to refine results.
\end{itemize}

\textbf{SLAP – Student Leave Application Portal}  
\textit{Flask, MySQL}
\begin{itemize}
    \item Developed a complete leave management system with role-based access for students and faculty.
    \item Added approval workflows, notifications, and history logs for real-time tracking.
\end{itemize}

\textbf{AI Music Player}  
\textit{Python}
\begin{itemize}
    \item Built an ML-powered music recommendation system that detects user mood and dynamically plays suitable songs.
    \item Integrated audio handling, playlist logic, and custom UI components for seamless interaction.
\end{itemize}

\textbf{voice-zen-dash}  
\textit{TypeScript, JavaScript, CSS, HTML}
\begin{itemize}
    \item Engineered a real-time voice assistant with support for multiple commands and integrations with popular services.
    \item Implemented natural language processing (NLP) algorithms to improve speech recognition accuracy.
\end{itemize}

\textbf{AI-Mobile-Manager}  
\textit{React Native, Expo}
\begin{itemize}
    \item Designed a mobile app for managing AI models and their applications on mobile devices.
    \item Implemented model training, deployment, and execution on device with real-time monitoring and analytics.
\end{itemize}

\end{document}
```

This resume focuses on the most relevant projects for a full-stack developer role.